insert title here

### 2020-12-09 slides.Rmd

---
title: "insert title here"
author:
output: powerpoint_presentation

---

>>>>

---
title: "insert title here"
author:
output: powerpoint_presentation
---

# NHL Background

## The National Hockey League (NHL)

-Each team plays 82 games per season
-This allows for every team to play each team at least twice

## The changes for the 2013-14 season

- Winnipeg Jets move from the Eastern to the Western confrence
- Columbus Blue jackets and Detroit Redwings move from the Wet to the East\

## The reasoning for the sampling

- Changes left the West with 2 divisions of 14 teams and the East with 2 divisions of 16 teams
- 8 teams from both confrences wer garunteed to make the playoffs
- The sampling is meant to test wheter or not it is more difficult to reach the playoffs as an eastern confrence team

# Extension 2017-18 season

- This season added the Vegas Golden Knights
- Now the west has 1 divion of 8 teams and one division of 7 teams
- This creates new probabillities for the required points to make it to the playoffs
